% Cover letter --- tailored to: Director of Information Technology,
% College of Agriculture and Life Sciences (CALS), Virginia Tech (Req. 536827).
% Styling matches Resume_UddhavGautam.tex. Compile: pdflatex CoverLetter_UddhavGautam.tex
\documentclass[11pt]{article}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{linkcolor}{RGB}{0,51,102}

\hypersetup{
 colorlinks=true,
 linkcolor=linkcolor,
 urlcolor=linkcolor,
 pdftitle={Uddhav P. Gautam - Cover Letter},
 pdfauthor={Uddhav P. Gautam},
 pdfborderstyle={/S/U/W 0}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\pagestyle{empty}

\begin{document}

% --- Letterhead (matches resume) ---
\begin{center}
{\LARGE\bfseries Uddhav P. Gautam}\\[0.4em]
{\small
+1 (919) 729-4141 \;\textbullet\;
\href{mailto:upgautam@vt.edu}{upgautam@vt.edu}
\;\textbullet\;
\href{https://uddhavpgautam.github.io}{Website}
\;\textbullet\;
\href{https://www.linkedin.com/in/uddhavpgautam/}{LinkedIn}
}
\end{center}

\vspace{3pt}
\hrule
\vspace{12pt}

\today

\vspace{8pt}

Search Committee, Director of Information Technology\\
College of Agriculture and Life Sciences \& Division of Information Technology\\
Virginia Tech, Blacksburg, Virginia

\vspace{6pt}
\textbf{Re: Director of Information Technology, College of Agriculture and Life Sciences (Requisition 536827)}

\vspace{6pt}
Dear Members of the Search Committee,

I am writing to apply for the Director of Information Technology position with the College of Agriculture and Life Sciences (Requisition 536827). I bring a decade of industry experience in software and IT, most recently as an architect and technical lead. I hold a Master's in Computer Science and am completing a PhD in Computer Engineering at Virginia Tech, where I work as a researcher and mentor students. I understand both the technology this role governs and the teaching, research, and Extension mission it supports.

As an architect and technical lead at Perficient, I led an eight-engineer Android team, with software engineers reporting to me, and set the engineering standards and architecture for a regulated platform that carried 30M+ users through the TD Ameritrade--Charles Schwab migration. Earlier, I spent four years as a system and network administrator, responsible for the infrastructure and daily operations of the organizations I supported. I have built CI/CD and DevSecOps pipelines and used production telemetry to drive measurable results, including a 40\% reduction in crash rate.

This position reports to both CALS and the Division of Information Technology and delivers services through a matrixed model. My work has had that structure throughout. In consulting I answered to both the client and my own firm; as a technical lead I set priorities and allocated resources across competing stakeholders; and as the founder of my own company I make budget and investment decisions directly. Because I run my own research at Virginia Tech, I also know what faculty need from research computing and data infrastructure, and I have taught here as a graduate teaching assistant.

I am a U.S. citizen and an honorably discharged veteran of the U.S. Army Reserve, where I held a Secret security clearance and can obtain one again. I require no visa sponsorship. I would welcome the chance to discuss how I can help CALS align its technology with the college's teaching, research, and Extension goals. Thank you for your consideration.

\vspace{8pt}
Sincerely,

\vspace{22pt}
Uddhav P. Gautam

\end{document}
