\documentclass[10pt]{article}
\usepackage[hmargin=1in, vmargin=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{needspace}
\usepackage{amssymb}
\usepackage{tikz}

% Academic CV color scheme: color is reserved for links; structure comes from weight and rules
\definecolor{sectioncolor}{RGB}{25,25,25}
\definecolor{linkcolor}{RGB}{0,51,102}
\definecolor{subtextcolor}{RGB}{90,90,90}
% Teaching-timeline role colors (validated categorical palette)
\definecolor{roleGRA}{HTML}{2A78D6}
\definecolor{roleGTA}{HTML}{1BAF7A}
\definecolor{roleSL}{HTML}{EB6834}

\hypersetup{
 colorlinks=true,
 linkcolor=linkcolor,
 urlcolor=linkcolor,
 pdftitle={Uddhav P. Gautam - Curriculum Vitae},
 pdfsubject={Academic CV: Trust Architectures for Software Systems -- Supply-Chain Intake Verification, Independent Verification of AI-Generated Code, OTA Security-Policy Evolution for Embedded Devices, eBPF and Linux Kernel},
 pdfauthor={Uddhav P. Gautam},
 pdfkeywords={software supply chain security, release assurance, XZ backdoor, AI-assisted development, verifier independence, DevSecOps, eBPF, Linux kernel, Bluetooth Low Energy, embedded security, OTA updates, Zephyr RTOS, mobile forensics, SCADA, Android development},
 pdfcreator={LaTeX with hyperref},
 pdfproducer={pdflatex},
 pdfborderstyle={/S/U/W 0}
}

\setlist[itemize]{leftmargin=1.2em, itemsep=3pt, topsep=3pt, parsep=0pt, partopsep=0pt}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titleformat{\section}{\large\bfseries\color{sectioncolor}}{}{0em}{}[\vspace{-2pt}\titlerule]
\setlength{\parindent}{0pt}
\pagestyle{empty}

\newcommand{\entry}[2]{%
 \par\needspace{2\baselineskip}\vspace{6pt}%
 {\noindent\textbf{#1}\hfill\mbox{\small\itshape #2}\par}%
}
\newcommand{\entrysub}[1]{%
 {\noindent\small\color{subtextcolor}\hspace*{8pt}#1\par}%
}
\newcommand{\thread}[1]{%
 \par\needspace{3\baselineskip}\vspace{6pt}%
 {\noindent\textbf{#1}\par}%
}
\newcommand{\cvsection}[1]{\needspace{5\baselineskip}\section*{#1}}

\begin{document}

\begin{center}
{\LARGE\bfseries Uddhav P. Gautam}\\[0.5em]
{\small
+1 (919) 729-4141 \;\textbullet\;
\href{mailto:upgautam@vt.edu}{upgautam@vt.edu}
\;\textbullet\;
\href{https://uddhavpgautam.github.io}{Website}
\;\textbullet\;
\href{https://scholar.google.com/citations?hl=en&user=Rbmabp4AAAAJ}{Google Scholar}
\;\textbullet\;
\href{https://github.com/uddhavpgautam}{GitHub}
\;\textbullet\;
\href{https://www.linkedin.com/in/uddhavpgautam/}{LinkedIn}
}
\end{center}


\begin{center}
{\small\textbf{Software veteran and open-source enthusiast} --- a decade as Software Engineer, Tech Lead, and Architect}\\[2pt]
{\small\itshape I build reliable, modular, scalable, and maintainable software using proven development best practices}
\end{center}

\vspace{10pt}

\cvsection{Career Objective}
{Seeking full-time opportunities in software architecture, technical leadership, or applied research.}


\cvsection{Research Interests}
\noindent\hangindent=3em\hangafter=1
\textbf{Security}: supply-chain compromise; fail-closed evidence semantics; BLE and embedded
post-compromise defense; mobile forensics; SCADA monitoring.

\hangindent=3em\hangafter=1
\textbf{Systems}: sandboxed eBPF extensibility; reboot-free OTA security-policy
lifecycles; verifier-to-runtime conformance.

\hangindent=3em\hangafter=1
\textbf{Software Engineering}: verifier independence for AI-assisted development; externalized evidence
contracts.

\cvsection{Professional Experience}
\entry{Android Technical Lead \& Architect, Perficient}{Jun 2021 -- May 2023}
\entrysub{Clients: TD Ameritrade, Charles Schwab}
\begin{itemize}
 \item Architected migration infrastructure supporting the transition of 30M+ TD Ameritrade users across Android,
 iOS, and web platforms to Charles Schwab systems after acquisition
 \item Led an 8-engineer Android team, established engineering standards, and maintained architecture and delivery
 documentation for a regulated codebase
 \item Migrated build configuration to Kotlin DSL, integrated static analysis, and restructured CI/CD pipeline 
 for multi-flavor production delivery
 \item Optimized a shared C++ core and the surrounding mobile performance pipeline, contributing to a measured
 40\% reduction in crash rate through production telemetry
\end{itemize}

\entry{Sr. Android Developer, Viper Design LLC}{Mar 2020 -- Feb 2021}
\begin{itemize}
 \item Built the full IoT software stack for Shark robot-vacuum products, from embedded firmware to
 cross-platform mobile applications
 \item Improved maintainability and testability by re-architecting the Android app around modular design,
 dependency injection, and serialization patterns
 \item Strengthened production stability through performance tuning, code shrinking, crash analytics, and
 automated testing
\end{itemize}

\entry{U.S. Army Reserve}{Apr 2019 -- Apr 2023}
\begin{itemize}
 \item Served four years and scored in the 96\textsuperscript{th} percentile on the Armed Forces Classification Test
\end{itemize}

\vspace{6pt}
\noindent
{\small\textit{\textbf{Prior roles}: 3 years as Android Developer; before that, 4 years as System/Network Administrator
after earning Microsoft and Ethical Hacking certifications.}}

\cvsection{Teaching \& Research Experience}
\noindent\textbf{Courses Taught}
\begin{itemize}[itemsep=4pt]
 \item \tikz[baseline=-0.55ex]{\fill[roleSL,rounded corners=1pt] (0,0) rectangle (1.7ex,1.7ex);}\; \textbf{Sole Lecturer} --- Android Apps Development, upper-division (UA Little Rock, Fall 2018);\, Discrete Mathematics (St.\ Lawrence College, Nepal, Spring 2014)
 \item \tikz[baseline=-0.55ex]{\fill[roleGTA,rounded corners=1pt] (0,0) rectangle (1.7ex,1.7ex);}\; \textbf{Graduate Teaching Assistant} --- Java Programming (Virginia Tech, Spring 2025);\, Operating Systems and Microprocessor Programming (UA Little Rock)
\end{itemize}

\vspace{7pt}
\noindent
\begin{tikzpicture}[
    lbl/.style={below,text=subtextcolor,font=\scriptsize,inner sep=2pt},
    inst/.style={above,font=\footnotesize\bfseries,inner sep=3pt}
  ]
  \def\h{0.54}
  % --- St.\ Lawrence College ---
  \begin{scope}
    \clip[rounded corners=3.5pt] (0,0) rectangle (2.3,\h);
    \fill[roleSL] (0,0) rectangle (2.3,\h);
  \end{scope}
  \node[inst] at (1.15,\h) {St.\ Lawrence College};
  \node[lbl]  at (1.15,0) {Spring 2014};
  % --- UA Little Rock ---
  \begin{scope}
    \clip[rounded corners=3.5pt] (2.8,0) rectangle (7.4,\h);
    \fill[roleGTA] (2.8,0) rectangle (5.1,\h);
    \fill[roleSL]  (5.1,0) rectangle (7.4,\h);
  \end{scope}
  \draw[white,line width=1pt] (5.1,0)--(5.1,\h);
  \node[inst] at (5.1,\h) {UA Little Rock};
  \node[lbl]  at (3.95,0) {Spring 2018};
  \node[lbl]  at (6.25,0) {Fall 2018};
  % --- Virginia Tech ---
  \begin{scope}
    \clip[rounded corners=3.5pt] (7.9,0) rectangle (14.8,\h);
    \fill[roleGRA] (7.9,0)  rectangle (10.2,\h);
    \fill[roleGTA] (10.2,0) rectangle (12.5,\h);
    \fill[roleGRA] (12.5,0) rectangle (14.8,\h);
  \end{scope}
  \draw[white,line width=1pt] (10.2,0)--(10.2,\h) (12.5,0)--(12.5,\h);
  \node[inst] at (11.35,\h) {Virginia Tech};
  \node[lbl]  at (9.05,0)  {Spring--Fall 2024};
  \node[lbl]  at (11.35,0) {Spring 2025};
  \node[lbl]  at (13.65,0) {Sum 2025--Fall 2026};
\end{tikzpicture}

\vspace{9pt}
\noindent{\footnotesize
\tikz[baseline=-0.55ex]{\fill[roleSL,rounded corners=1pt] (0,0) rectangle (1.7ex,1.7ex);}\, Sole Lecturer \hspace{1.4em}
\tikz[baseline=-0.55ex]{\fill[roleGTA,rounded corners=1pt] (0,0) rectangle (1.7ex,1.7ex);}\, Teaching Assistant (GTA) \hspace{1.4em}
\tikz[baseline=-0.55ex]{\fill[roleGRA,rounded corners=1pt] (0,0) rectangle (1.7ex,1.7ex);}\, Research Assistant (GRA)}

\cvsection{Software}
Founder and sole developer, RGR Innovate LLC (2024 -- Present). Three free, ad-free Android applications
published as a public service on
\href{https://play.google.com/store/apps/dev?id=6755050398195804153}{Google Play}.
\begin{itemize}[itemsep=3pt]
 \item \textbf{Earthquakes by RGR}: real-time seismic mapping over USGS GeoJSON feeds with location
 search and radius/magnitude filtering (Google Maps, Google Places)
 \item \textbf{SmartConvert}: fully offline multi-tool for document scanning with edge detection,
 image/unit/color conversion, screen ruler, and ARCore room measurement (no accounts, no network required)
 \item \textbf{Passport \& ID Photo Studio}: print-ready passport, visa, and ID photos for 155+ countries
 using on-device face detection, background removal, and automated compliance checks
\end{itemize}

\cvsection{Technical Expertise}
\begin{multicols}{2}
\noindent\textbf{Systems \& Kernel}
\begin{itemize}[topsep=1pt,noitemsep]
 \item eBPF (TC, XDP, tracing, uBPF sandbox)
 \item Linux kernel development
 \item C/C++, Python
\end{itemize}

\vspace{4pt}
\noindent\textbf{Embedded \& IoT Security}
\begin{itemize}[topsep=1pt,noitemsep]
 \item BLE protocol security
 \item Zephyr RTOS, Nordic nRF52840
 \item Authenticated OTA updates
 \item Runtime policy enforcement
\end{itemize}

\columnbreak

\noindent\textbf{Security \& Assurance}
\begin{itemize}[topsep=1pt,noitemsep]
 \item Software supply-chain security
 \item Reproducible builds, SBOM, SARIF
 \item Trivy, OWASP Dep.-Check, MVT
 \item Mobile forensics (Cellebrite UFED)
 \item SCADA (DNP3, Modbus, IEC 61850)
\end{itemize}

\vspace{4pt}
\noindent\textbf{Software \& Infrastructure}
\begin{itemize}[topsep=1pt,noitemsep]
 \item Kotlin, Java, Android development
 \item DevSecOps, Docker
 \item AWS, GCP, Firebase
 \item Elasticsearch, Logstash, Filebeat
\end{itemize}
\end{multicols}

\cvsection{Education} 
\entry{Ph.D. Computer Engineering, Virginia Tech \textmd{(GPA: 4.0/4.0)}}{2024 -- Present} 
\entrysub{Advisors: \href{https://ece.vt.edu/people/profile/wangh.html}{Haining Wang}, \href{https://security.vt.edu/about/staff/randy-marchany/}{Randy Marchany}} 
\vspace{-3pt} 
\entry{M.S. Computer Science, UA Little Rock \textmd{(GPA: 3.58/4.0)}}{2015 -- 2017} 
\vspace{-3pt} 
\entry{B.S. Computer Science, Tribhuvan University, Nepal \textmd{(GPA: 3.91/4.0)}}{2009 -- 2013}

\cvsection{Honors \& Awards}
\begin{itemize}[itemsep=3pt]
 \item \textbf{UA Little Rock} --- 1st Place: Complete Societal Award, Societal Impact Award, Best
 Graduate Project Award; 2nd Place: Personal Achievement Award \& TechLaunch Entrepreneurial Team
 Projects Competition
 \item \textbf{Tribhuvan University, Nepal} --- Top-5 Final-Year Project Award, Nepal Telecom Authority (NTA)
\end{itemize}


\cvsection{Publications}
\thread{Manuscripts Under Review}
\begin{itemize}[itemsep=3pt]
 \item \textbf{Uddhav P. Gautam}, et al. ``Breaking Self-Referential Trust in Source Releases:
 A Parity Gate for OS Package Supply Chains.'' \textit{Ready for submission, USENIX Security 2027.}
 Artifact: {\color{subtextcolor}\textit{link to be added}}
 \item \textbf{Uddhav P. Gautam}, et al. ``Breaking Self-Referential Trust with AIE Verification in
 AI-Assisted Development and Release Assurance.'' \textit{Under review, ICSE 2027.}
 Artifact: \href{https://figshare.com/s/d0871296649a28ecd956}{figshare}
 \item \textbf{Uddhav P. Gautam}, et al. ``ZeroDown: Firmware-Decoupled OTA Security-Policy Updates
 for MCU-Class BLE Peripherals.'' \textit{Under review, EuroSys 2027.}
 Artifact: {\color{subtextcolor}\textit{link to be added}}
 \item \textit{Sahil Dudani}, \textbf{Uddhav P. Gautam}, et al. ``Ghost in the Device: The Parallel
 World of Spy Apps Forensics.'' \textit{Under review, Forensic Science International: Digital Investigation, Elsevier.}
 \item \textit{Ashraf Saeed}, \textbf{Uddhav P. Gautam}, et al. ``AI-Code Verification Readiness in
 CS1: A Seeded-Flaw Diagnostic.'' \textit{Under review, Koli Calling.}
\end{itemize}

\thread{Peer-Reviewed Publications}
\begin{itemize}[itemsep=3pt]
 \item Milo Craun, Khizar Hussain, \textbf{Uddhav P. Gautam},
 et al. ``Eliminating eBPF Tracing Overhead
 on Untraced Processes.'' \textit{Proc. ACM SIGCOMM Workshop on eBPF \& Kernel Ext.}, 2024.
 DOI: \href{https://doi.org/10.1145/3672197.3673431}{10.1145/3672197.3673431}
 \item Syed Akailvi, \textbf{Uddhav P. Gautam}, et al.
 ``HELOT---Hunting Evil Life in Operational Technology.''
 \textit{IEEE Trans. Smart Grid}, vol. 14, no. 4, pp. 3058--3071, Jul. 2023.
 DOI: \href{https://doi.org/10.1109/TSG.2022.3222261}{10.1109/TSG.2022.3222261}
\end{itemize}


\cvsection{Certifications}
\noindent
{\small Software Architecture, CI/CD \& DevOps, Deep Learning (NVIDIA), Java/Kotlin Design Patterns,
React Native, Scrum Master, Decision Making, Delegating Tasks, and multiple Microsoft certifications
(full list on \href{https://www.linkedin.com/in/uddhavpgautam/}{LinkedIn}).}

\cvsection{References}
\begin{itemize}[itemsep=2pt] 
  \item \textbf{Haining Wang} Prof., Bradley Dept.\ of Electrical \& Computer Engineering, Virginia Tech, \href{mailto:hnw@vt.edu}{hnw@vt.edu}, \mbox{(757) 813-4390}
  \item \textbf{Randy Marchany} CISO \& Director, IT Security Lab, Virginia Tech, \href{mailto:marchany@vt.edu}{marchany@vt.edu}, \mbox{(540) 250-7681}
  \item \textbf{Brad Tilley} Director, Security Architecture \& Red Team, Virginia Tech, \href{mailto:btilley@vt.edu}{btilley@vt.edu}, \mbox{(540) 231-3133}
\end{itemize}

\end{document}
